---
format: 
  dashboard
orientation: rows
scrolling: true 
---

```{r, include = FALSE}
# Load Libraries
library(plotly)
library(here)
library(dplyr)
library(ggplot2)
library(DT)
library(crosstalk)
library(readxl)
library(tidyr)
library(leaflet)
library(sf)
```

<!-- Load data -->
```{r, include=FALSE}
path <- here::here("data", "prepped_data.RData")
load(path)
```

<!-- Function for creating the sub-category plots -->

```{r, include=FALSE}
sub_cat_plot <- function(df, shared_env, title, fill_color){
  max_count <- max(df$count_by_sub)
  # Set end value of y-axis range
  r <- max_count + 6
  
  # Conditionally set the label nudge distance
  if(max_count< 11){
    nudge <- 0.2
  }
  else {
    nudge <- 1
  }
  gg_plot <- ggplot(shared_env, aes(y = sub_category,
                                 text = paste(sub_cat_text)
                                 )) +
    geom_bar(fill = fill_color) + 
    geom_text(aes(label = ..count..), stat = "count", 
              nudge_x = nudge, color = fill_color) +
    scale_fill_discrete(drop=FALSE) +
    scale_y_discrete(drop = FALSE) + theme_classic() +
    theme(axis.ticks.x = element_blank(),
          axis.line = element_blank())
  
  ggplotly(gg_plot, tooltip = c("text")) %>%
    layout(hoverlabel = list(align="left",
                             bgcolor = fill_color),
           title = title,
           margin = list(t = 50), 
           xaxis = list(showticklabels = FALSE,
                        title = FALSE,
                        range = list(0, r),
                        fixedrange = TRUE
                        ),
           yaxis = list(showticklabels = TRUE,
                       title = FALSE,
                       fixedrange = TRUE),
           showlegend = F) %>%
    style(hoverinfo = 'none', traces = c(1),
          textposition = "none") %>%
    highlight(on = "plotly_click", off = "plotly_doubleclick")

}
```

<!-- Intercept Plot Function -->

```{r, include=FALSE}
intercept_plot <- function(df, shared_env, fill_color){
  r <- df %>% as.data.frame() %>% select(count_by_int) %>% max() + 6
  
  gg_plot <- ggplot(shared_env, aes(y = intercept,
                                 text = paste(int_cat_text)
                                 )) +
    geom_bar(color = fill_color, fill = "white") + 
    geom_text(aes(label = after_stat(count)), stat = "count", 
              nudge_x = 1, color = "#545352") +
    scale_y_discrete(drop = FALSE) + theme_classic() +
    theme(axis.ticks.x = element_blank(),
          axis.line = element_blank())
  
  
  ggplotly(gg_plot, tooltip = c("text")) %>%
    layout(hoverlabel = list(align="left",
                             bgcolor = fill_color),
           margin = list(t = 50), 
           xaxis = list(showticklabels = FALSE,
                        title = FALSE,
                        range = list(0, r),
                        fixedrange = TRUE
                        ),
           yaxis = list(showticklabels = TRUE,
                       title = FALSE,
                       fixedrange = TRUE),
           showlegend = F) %>%
    style(hoverinfo = 'none', traces = c(1),
          textposition = "none") %>%
    highlight(on = "plotly_click", off = "plotly_doubleclick") 
}               
```

<!-- Function for creating downloadable DT tables -->

```{r, include=FALSE}
dtable <- function(shared_env){
    dt_table <- shared_env %>% datatable(
      colnames = c("Program", "Agency",  "Need Category", 
                   "Count by Need category", "Sub Category", "Count by Sub-category",
                   "Intercept", "Intercept Code", "Count by Intercept", 
                   "Count by Intercept (by Need)", "Zipcode", "Count by Zipcode",
                   "Count by Zip Code (by Need)", "Longitude", "Latitude", 
                   "Geometry", "Text Label", "Text Label (by Need)"),
      extensions = "Buttons",
      options = list(
        columnDefs = list(list(visible = FALSE, targets = c(4,9,12,14,15,16,17,18))),
        buttons = c("csv", "excel"),
        text = "Download",
        # paging = TRUE,
        # lengthMenu = c(5, 10, 25),
        # pageLength = 10,
        dom = "Bfrtip",
        scrollX = TRUE
      )
    )
  dt_table 
}
```


# All {orientation="rows" scrolling="true"}

```{r, echo=FALSE}
# For crosstalk
shared_data_all <- SharedData$new(all, key = ~program)
```

## Row 

### Column{.tabset}
```{r, echo = FALSE}
#| title: By Need Category
r <- max(all$count_by_main) + 6

all_plot <- ggplot(shared_data_all, aes(y = main_category,
                               text = paste(main_cat_text)
                               )) +
  geom_bar(color = "#003f5c", fill = "white") + 
  geom_text(aes(label = after_stat(count)), stat = "count", 
            nudge_x = 1, color = "#545352") +
  # scale_fill_discrete(drop=FALSE) +
  scale_y_discrete(drop = FALSE) + theme_classic() +
  theme(axis.ticks.x = element_blank(),
        axis.line = element_blank())




ggplotly(all_plot, tooltip = c("text")) %>%
  layout(hoverlabel = list(align="left",
                           bgcolor = "#003f5c"),
         title = "Asset Map Main Categories",
         margin = list(t = 50), 
         xaxis = list(showticklabels = FALSE,
                      title = FALSE,
                      range = list(0, r),
                      fixedrange = TRUE
                      ),
         yaxis = list(showticklabels = TRUE,
                     title = FALSE,
                     fixedrange = TRUE),
         showlegend = F) %>%
  style(hoverinfo = 'none', traces = c(1),
        textposition = "none") %>%
  highlight(on = "plotly_click", off = "plotly_doubleclick")

```

```{r, echo = FALSE}
#| title: By Intercept
intercept_plot(all, shared_data_all, "#ffa600")               
```

```{r, echo = FALSE}
#| title: By Zipcode

bscols(widths = c(12),
  list(
    filter_select("zip", "Zipcodes", shared_data_all, ~zipcode)
  )

)
```

### Column

::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the all need categories.

Follow this [link](definitions.html) to see the definitions for the categories used in classifying the data.

The data can be filtered by zipcode, sub-category, or intercept category and downloaded in either CSV or Excel format.
:::

## Row
```{r, echo = FALSE}
#| title: Data
dt_table <- shared_data_all %>%
  datatable(
    colnames = c("Program", "Agency",  "Need Category", 
                 "Count by Need category", "Sub Category", 
                 "Intercept", "Intercept Code", "Count by Intercept", 
                 "Count by Intercept (by Need)", "Zipcode", "Count by Zipcode",
                 "Count by Zip Code (by Need)", "Longitude", "Latitude", 
                 "Geometry", "Text Label", "Text Label (by Need)"),
    extensions = "Buttons",
    options = list(
      columnDefs = list(list(visible = FALSE, targets = c(9,12,13,14,15,16,17))),
      buttons = c("csv", "excel"),
      text = "Download",
      # paging = TRUE,
      # lengthMenu = c(5, 10, 25),
      # pageLength = 10,
      dom = "Bfrtip",
      scrollX = TRUE
    )
  )
dt_table
```

# Behavioral Health Services {orientation="rows" scrolling="true"}

```{r, echo=FALSE}
# For crosstalk
shared_data_bhs <- SharedData$new(bhs, key = ~program)
```

## Row 
### Column{.tabset}
```{r, echo=FALSE}
#| title: By Sub-category
cols <- c("#003f5c",  "#2c4875", "#58508d", "#8a508f", "#bc5090", "#de5a79", "#ff6361", "#ff8531", "#ffa600")
sub_cat_plot(bhs, shared_data_bhs, "Behavioral Health Services", "#003f5c")
```

```{r}
#| title: By Intercept
intercept_plot(bhs, shared_data_bhs, "#003f5c")
```


```{r, echo = FALSE}
#| title: By Zipcode

bscols(widths = c(12),
  list(
    filter_select("zip", "Zipcodes", shared_data_bhs, ~zipcode)
  )

)
                
```

### Column

::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the behavioral health need category.

Follow this [link](definitions.html#behavioral-health-services) to see the definitions for the categories used in classifying the data.

The data can be filtered by zip code, sub-category, or intercept category.

Click a bar to select a category and double-click outside the bar to deselect.

Filtered or unfiltered data can be downloaded in either CSV or Excel format
:::

## Row

```{r, echo = FALSE}
#| title: Data
dtable(shared_data_bhs)
```
# Substance Use Treatment {orientation="rows" scrolling="true"}

```{r, echo=FALSE}
# For crosstalk
shared_data_sut <- SharedData$new(sut, key = ~program)
```

## Row 
### Column{.tabset}
```{r, echo=FALSE}
#| title: By Sub-category
cols <- c("#003f5c",  "#2c4875", "#58508d", "#8a508f", "#bc5090", "#de5a79", "#ff6361", "#ff8531", "#ffa600")
sub_cat_plot(sut, shared_data_sut, "Substance Use Treatment", "#2c4875")
```

```{r}
#| title: By Intercept
intercept_plot(sut, shared_data_sut, "#2c4875")
```


```{r, echo = FALSE}
#| title: By Zipcode

bscols(widths = c(12),
  list(
    filter_select("zip", "Zipcodes", shared_data_sut, ~zipcode)
  )

)
                
```

### Column

::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the substance use treatment need category.

Follow this [link](definitions.html#substance-use-treatment) to see the definitions for the categories used in classifying the data.

The data can be filtered by zip code, sub-category, or intercept category.

Click a bar to select a category and double-click outside the bar to deselect.

Filtered or unfiltered data can be downloaded in either CSV or Excel format
:::

## Row

```{r, echo = FALSE}
#| title: Data
dtable(shared_data_sut)
```

# Housing Assistance {orientation="rows" scrolling="true"}

```{r, echo=FALSE}
# For crosstalk
shared_data_ha <- SharedData$new(ha, key = ~program)
```

## Row 
### Column{.tabset}
```{r, echo=FALSE}
#| title: By Sub-category
cols <- c("#003f5c",  "#2c4875", "#58508d", "#8a508f", "#bc5090", "#de5a79", "#ff6361", "#ff8531", "#ffa600")
sub_cat_plot(ha, shared_data_ha, "Housing Assistance", "#58508d")
```

```{r}
#| title: By Intercept
intercept_plot(ha, shared_data_ha, "#58508d")
```


```{r, echo = FALSE}
#| title: By Zipcode

bscols(widths = c(12),
  list(
    filter_select("zip", "Zipcodes", shared_data_ha, ~zipcode)
  )

)
                
```

### Column

::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the housing assistance need category.

Follow this [link](definitions.html#housing-assistance) to see the definitions for the categories used in classifying the data.

The data can be filtered by zip code, sub-category, or intercept category.

Click a bar to select a category and double-click outside the bar to deselect.

Filtered or unfiltered data can be downloaded in either CSV or Excel format
:::

## Row

```{r, echo = FALSE}
#| title: Data
dtable(shared_data_ha)
```
# Healthcare Services {orientation="rows" scrolling="true"}

```{r, echo=FALSE}
# For crosstalk
shared_data_hcs <- SharedData$new(hcs, key = ~program)
```
::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the healthcare services need category.

Follow this [link](definitions.html#healthcare-services) to see the definitions for the categories used in classifying the data.

There is currently no data to display for this need category.
:::

# Community Policing Initiatives {orientation="rows" scrolling="true"}

```{r, echo=FALSE}
# For crosstalk
shared_data_cpi <- SharedData$new(cpi, key = ~program)
```
::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the community policing intiative need category.

Follow this [link](definitions.html#community-policing-initiatives) to see the definitions for the categories used in classifying the data.

There is currently no data to display for this need category.
:::

# Legal Aid & Advocacy {orientation="rows" scrolling="true"}
```{r, echo=FALSE}
# For crosstalk
shared_data_laa <- SharedData$new(laa, key = ~program)
```

## Row 
### Column{.tabset}
```{r, echo=FALSE}
#| title: By Sub-category
cols <- c("#003f5c",  "#2c4875", "#58508d", "#8a508f", "#bc5090", "#de5a79", "#ff6361", "#ff8531", "#ffa600")
sub_cat_plot(laa, shared_data_laa, "Legal Aid & Advocacy", "#de5a79")
```

```{r}
#| title: By Intercept
intercept_plot(laa, shared_data_laa, "#de5a79")
```


```{r, echo = FALSE}
#| title: By Zipcode

bscols(widths = c(12),
  list(
    filter_select("zip", "Zipcodes", shared_data_laa, ~zipcode)
  )

)
                
```

### Column

::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the legal aid & advocacy need category.

Follow this [link](definitions.html#legal-aid-and-advocacy) to see the definitions for the categories used in classifying the data.

The data can be filtered by zip code, sub-category, or intercept category.

Click a bar to select a category and double-click outside the bar to deselect.

Filtered or unfiltered data can be downloaded in either CSV or Excel format
:::

## Row

```{r, echo = FALSE}
#| title: Data
dtable(shared_data_laa)
```

# Legal Diversion Supports {orientation="rows" scrolling="true"}

```{r, echo=FALSE}
# For crosstalk
shared_data_lds <- SharedData$new(lds, key = ~program)
```

## Row 
### Column{.tabset}
```{r, echo=FALSE}
#| title: By Sub-category
cols <- c("#003f5c",  "#2c4875", "#58508d", "#8a508f", "#bc5090", "#de5a79", "#ff6361", "#ff8531", "#ffa600")
sub_cat_plot(lds, shared_data_lds, "Legal Diversion Supports", "#ff6361")
```

```{r}
#| title: By Intercept
intercept_plot(lds, shared_data_lds, "#ff6361")
```


```{r, echo = FALSE}
#| title: By Zipcode

bscols(widths = c(12),
  list(
    filter_select("zip", "Zipcodes", shared_data_lds, ~zipcode)
  )

)
                
```

### Column

::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the legal diversion supports need category.

Follow this [link](definitions.html#legal-diversion-supports) to see the definitions for the categories used in classifying the data.

The data can be filtered by zip code, sub-category, or intercept category.

Click a bar to select a category and double-click outside the bar to deselect.

Filtered or unfiltered data can be downloaded in either CSV or Excel format
:::

## Row

```{r, echo = FALSE}
#| title: Data
dtable(shared_data_lds)
```

# Re-Entry Support {orientation="rows" scrolling="true"}

```{r, echo=FALSE}
# For crosstalk
shared_data_res <- SharedData$new(res, key = ~program)
```

## Row 
### Column{.tabset}
```{r, echo=FALSE}
#| title: By Sub-category
cols <- c("#003f5c",  "#2c4875", "#58508d", "#8a508f", "#bc5090", "#de5a79", "#ff6361", "#ff8531", "#ffa600")
sub_cat_plot(res, shared_data_res, "Re-Entry Support", "#ff8531")
```

```{r}
#| title: By Intercept
intercept_plot(res, shared_data_res, "#ff8531")
```


```{r, echo = FALSE}
#| title: By Zipcode

bscols(widths = c(12),
  list(
    filter_select("zip", "Zipcodes", shared_data_res, ~zipcode)
  )

)
                
```

### Column

::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the re-entry support need category.

Follow this [link](definitions.html#reentry-support) to see the definitions for the categories used in classifying the data.

The data can be filtered by zip code, sub-category, or intercept category.

Click a bar to select a category and double-click outside the bar to deselect.

Filtered or unfiltered data can be downloaded in either CSV or Excel format
:::

## Row

```{r, echo = FALSE}
#| title: Data
dtable(shared_data_res)
```

# Community Engagement & Awareness {orientation="rows" scrolling="true"}

```{r, echo=FALSE}
# For crosstalk
shared_data_cea <- SharedData$new(cea, key = ~program)
```

::: {.card title="Notes for Dashboard Use"}
This dashboard visualizes data for the community engagement and awareness need category.

Follow this [link](definitions.html#community-engagement-and-awareness) to see the definitions for the categories used in classifying the data.

There is currently no data to display for this need category.
:::
